\documentclass[12pt]{article}

\usepackage{geometry}
 \geometry{
 a4paper,
 total={170mm,257mm},
 left=20mm,
 top=30mm,
 bottom=30mm,
 }
\usepackage{xcolor}

\definecolor{shadecolor}{RGB}{150,150,150}
\newcommand{\mybox}[1]{\par\noindent\colorbox{shadecolor}
{\parbox{\dimexpr\textwidth-2\fboxsep\relax}{#1}}}

\begin{document}
\begin{LARGE}
\noindent\textbf{Himesh Jain}
\end{LARGE}\\
Student at The LNM Institute of Information Technology\\
\textcolor{gray}{himeshjain13@gmail.com}\\
+91*876964646133

\noindent\hrulefill \\
\begin{large}
\mybox{\textbf{Education}}
\end{large}
\\
\textbf{The LNM Institute of Information Technology}\\
B.Tech, Computer Science, 2015 - 2019\\
\textcolor{gray}{CGPA: 7.8/10}\\
\textbf{St. Xavier Sr. School, Jaipur}\\
High School, Science, 2003 - 2015\\
\hrulefill
\begin{large}
\mybox{\textbf{Internships}}
\end{large}
\\
\textbf{LadduShaddu Inc. (Gulukul, USA)}\\
July 2017 - September 2017\\
Worked as the main web developer on the company's website. As part of the it, worked on the full stack of the main website as well as an accompanying blog.\\
\textcolor{gray}{https://gulukul.com}\\
\hrulefill
\begin{large}
\mybox{\textbf{Position of Responsibility}}
\end{large}
\\
\textbf{Core Team Member}\\
Imagination\\
College's Photography Club\\
\hrulefill
\begin{large}
\mybox{\textbf{Projects}}
\end{large}
\\
\textbf{PlanIt}\\
\textcolor{gray}{https://github.com/HJain13/plan-it}\\
A web app project about making an Online Trip/Outing package (comprehensive) provider system  complete with Login/Register/Buying/Collaboration functionality. Front end was created using React, Bulma framework (CSS). Back end was created using NodeJs (Express) and Used MongoDB as a database.\\
\textbf{BookMark}\\
\textcolor{gray}{https://github.com/HJain13/BookMark}\\
Online Bookstore complete with an user management , book management and as well as order management system. Front end was created using skeleton framework (CSS) , html and jsp. Back end was created using Java and MySQL.\\
\textbf{RoboVac}\\
\textcolor{gray}{https://github.com/HJain13/RoboVac}\\
In this project Our team designed ISA, Assembler, Machine Simulator and Microarchitecture Design for a Theoretical Automated Robotic Vacumm Cleaner. This was developed by our group (4 members) as a submission to course project of COA Lab in 2nd year of our CSE Major.\\
\textbf{Primitive-Databse}\\
\textcolor{gray}{https://github.com/HJain13/Primitive-Databse}\\
A simple C program to emulate some rudimentary functionalities of a full blown DBMS. It was a mini Project For DBMS Course (CSE Major).\\
\textbf{Nachos}\\
\textcolor{gray}{https://github.com/HJain13/Nachos}\\
Mini Project using APIs and Content aggregation\\
\hrulefill
\begin{large}
\mybox{\textbf{Skills}}
\end{large}
\begin{itemize}
  \item React.js
  \item Express
  \item Node.js
  \item MongoDB
  \item HTML5
  \item CSS3 and its Frameworks
  \item Javascript (libraries)
  \item Photography
  \item Adobe Photoshop

\end{itemize}
\begin{large}
\mybox{\textbf{Honors and Awards}}
\end{large}
\\
\textbf{Honorable Mention in Space Settlement Design Contest}\\
NASA Ames Research Center\\
April 2013\\
Our team took part in Space Settlement Design Contest, conducted by NASA Ames Research Center. The aim was to design a fully habitable Space Settlement. Our project, 'Serenity'  bagged an Honorable Mention.\\
\hrulefill
\end{document}